Approximation as Differentiation

### 2025-04-02 notes/sec/cmon-enriched.tex
Various tweaks.

We note that if a category $C$ is $\CMon$-enriched, then:
\begin{enumerate}
\item Every hom-object $\Hom{C}{A}{B}$ is a commutative monoid of morphisms; we write $\zero_{A,B}$ (zero
morphism) for the unit, and $+_{A,B}$ (addition of morphisms) for the binary operation.
\item Composition is \emph{bilinear}, i.e.~given by a family of morphisms $\Hom{C}{B}{C} \tensor
\Hom{C}{A}{B} \to \Hom{C}{A}{C}$ in $\CMon$ that preserve the additive structure in $\Hom{C}{B}{C}$ and
$\Hom{C}{A}{B}$ separately:

@@

$\CMon$ is closed monoidal, and so enriched over itself. More specifically every hom-object $\Hom{CMon}{A}{B}$
is a commutative monoid of commutative monoid homomorphisms where:

\begin{enumerate}
\item the unit $0$ is the constant homomorphism sending every element of $A$ to $\varepsilon_B$;
\item addition of morphisms $+$ is defined pointwise so that $(f + g)(a) = f(a) + g(a)$.
\end{enumerate}

\begin{proposition}
If $C$ is $\CMon$-enriched then for any category $D$ the functor category $\Func{D}{C}$ is $\CMon$-enriched.
\end{proposition}

>>>>

Recall that if a category $C$ is $\CMon$-enriched, then:
\begin{enumerate}
\item Every hom-object $\Hom{C}{A}{B}$ is a commutative monoid of morphisms; we write $\zero_{A,B}$ (zero
morphism) for the unit, and $+_{A,B}$ (addition of morphisms) for the binary operation.
\item Composition is \emph{bilinear}, i.e.~given by a family of morphisms $\Hom{C}{B}{C} \tensor
\Hom{C}{A}{B} \to \Hom{C}{A}{C}$ in $\CMon$ that preserve the additive structure in $\Hom{C}{B}{C}$ and
$\Hom{C}{A}{B}$ separately:

@@

Because $\CMon$ is closed monoidal, it is enriched over itself; every hom-object $\Hom{CMon}{A}{B}$ is a
commutative monoid where:

\begin{enumerate}
\item the unit $0$ is the constant homomorphism sending every element of $A$ to $\varepsilon_B$;
\item the binary operation $+$ is pointwise addition of homomorphisms $(f + g)(a) = f(a) + g(a)$.
\end{enumerate}

\begin{proposition}
If $C$ is $\CMon$-enriched then any functor category $\Func{D}{C}$ is $\CMon$-enriched.
\end{proposition}
